---
title: "Homework Assignment #1"
---


**Your Name**:
**Your Email**:


In this homework assignment we will be focusing on data analysis and visualization with the `tidyverse`.

Before starting this assignment, please download `R` and `RStudio Desktop` on your computer. Both are open-source and free to use.

Detailed installation instructions can be found at https://www.datacamp.com/community/tutorials/installing-R-windows-mac-ubuntu

After completing the assignment, please upload this file (`.Rmd`) to Blackboard as your submission.


# Load Packages and Data

The `R` code chunk below will load the `tidyverse` and `tidymodels` packages as well as an `auto_claims` data set.

**Note:** If you get an error running the code below, make sure that you have installed the required packages in your RStudio desktop environment. To install any package, navigate to the bottom right pane of RStudio, select the `Packages` tab and click the `Install` button.


```{r}
library(tidyverse)

auto_claims <- read_rds(url('https://gmudatamining.com/data/auto_claims.rds'))
```



The `auto_claims` data contains information on auto accident claims processed by an insurance company in the western part of the United States.

Each row represents a claim made by a customer and includes customer demographics, their policy characteristics, monthly premium, vehicle information, claim amount, and [customer lifetime value](https://en.wikipedia.org/wiki/Customer_lifetime_value)


```{r}
auto_claims
```



# Problem 1

Write one expression using `dplyr` functions and the `>%>` operator to create the summary table below.

This table contains the number of claims, average claim amount (`total_claim_amount` variable), and average customer lifetime value by `customer_state` and `months_since_last_claim` binned into 12 month categories.

**Hint**: You will need to create the `month_category` variable using `cut_width()` before you calculate the summaries by groups.


```{r}

auto_claims %>% 
  mutate(months_category = ---- ) %>% 
  group_by( ---- ) %>% 
  summarise( ---- )


```



# Problem 2

Write one expression using `dplyr` functions and the `>%>` operator to create the summary table below. 

This table contains the minimum, median, and maximum values of `total_claim_amount` by `vehicle_class` for the 10 largest `total_claim_amount` values within each `vehicle_class` category.


```{r}

auto_claims %>% 
  group_by( ---- ) %>% 
  top_n( ---- ) %>% 
  summarise( ---- )

  
```




# Problem 3

Use `ggplot` to create the data visualization below. Please use `alpha = 0.25` and `color = '#006EA1` within your `geom` function to match the points below.

```{r}







```




# Problem 4

Use `ggplot` to create the data visualization below.


```{r}






```




# Problem 5

Use `ggplot` to create the data visualization below. The number of bins in the histogram should be set to 15.


```{r}


```

